Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-16 manuscript/manuscript.Rmd
Fix variables for packaging

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- ../../Mendeley/library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 5000?
---

>>>>

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- ../../../Mendeley/library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 5000?
---
